Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression

### 2024-12-03 paper/paper.qmd
prose checked
prose checked

Seasonal data also show that bike usage significantly decreases during winter, approaching zero, while increasing steadily during spring and summer, peaking in August and September during the start of the academic year. This suggests the need for proactive and dynamic adjustments in bike supply. During the start of the academic year, expanding station capacity and offering user-friendly navigation services can help new and returning students quickly familiarize themselves with the system. In winter, efforts should focus on improving station infrastructure (e.g., anti-freeze facilities) and maintaining safety under cold conditions. Additionally, by utilizing predictive analytics to forecast station-specific demand fluctuations, resources can be optimized in advance, minimizing inconveniences caused by bike shortages or overcrowded parking during peak times.

@@

To simplify the dataset’s structure and reduce its size for efficient processing, the study extracted only the necessary variables, including `trip_start_time` and `from_station_name`, which are critical for subsequent analysis.

>>>>

Seasonal data also show that bike usage significantly decreases during winter, approaching zero, while increasing steadily during spring and summer, peaking in August and September during the start of the academic year. This suggests the need for proactive and dynamic adjustments in bike supply. During the start of the academic year, expanding station capacity and offering user-friendly navigation services can help new and returning students quickly familiarize themselves with the system. In winter, efforts should focus on improving station infrastructure (e.g., anti-freeze facilities) and maintaining safety under cold conditions. Additionally, by utilizing predictive analytics to forecast station-specific demand fluctuations, resources can be optimized, minimizing inconveniences caused by bike shortages or overcrowded parking during peak times.

@@

To simplify the dataset’s structure and reduce its size for efficient processing, the study extracted only the necessary variables, including `trip_start_time` and `from_station_name`, which are important for subsequent analysis.
